\documentclass{article}               % article class
\begin{document}                      % Begin document text

\section*{Boda boda riders Data Collection Concept}

Data is gathered on boda boda riders around Uganda so that it can be used to analyze important metrics.\\
\\This information will help us know the problems faced by the different riders, the most congested stages and how safe the riders are so that the government can plan better for them.\\
\\The information will also help the authorities make well informed decisions and limit the chances of backlash from the riders since they will be coming from a position of knowledge and understanding.

\section*{Problem solved from collection of this data}
Management of boda boda industry in the country most especially the city is a vital and delicate issue that needs to be handled carefully not only due to the sheer number of individuals employed by it but also due to the volatility of the said individuals therefore the acquisition of this data will help in its management.

\subsection*{Type of Data Collected}
 We shall also collect the following data:

\begin{enumerate}
\item{\subsubsection*{Photo}}
A photo taken to identify the rider.
\item{\subsubsection*{First, Last Name, Date of Birth and Location of the Boda Boda Stage.}}
These are some of the fields we will use to identify the riders.
\item{\subsubsection*{Registration Number}}
This will used to uniquely identify the riders.
\item{\subsubsection*{Does he have a helmet?}}
We will use this to know how safe the boda boda riders are.
\item{\subsubsection*{An Audio About General problems faced by Boda boda riders and Suggested Solutions}}
This will help us understand what needs to be improved or changed for the boda boda riders.
\end{enumerate}



\end{document}